\documentclass[BCOR13mm,DIV15]{scrartcl}
% \documentclass[12pt]{IEEEtran}

% General document formatting
\usepackage[margin=0.7in, bottom=.7in]{geometry}
% \usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}

\usepackage[T1]{fontenc}
\usepackage{helvet}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\graphicspath{{../Figures/} {../Figures/Models/}{../Figures/PreProcessing/}}

\usepackage{lipsum}
\usepackage{natbib}

% \usepackage[
% backend=biber,
% style=alphabetic,
% citestyle=authoryear
% ]{biblatex}

% \addbibresource{EEE4022S.bib} %Imports bibliography file




\usepackage{xcolor}






%Dark mode pdf
\pagecolor[rgb]{0.15,0.14,0.125} % Dark Grey
\definecolor{myTextColour}{rgb}{0.9,0.9,0.8}


% Light Theme
% \definecolor{myTextColour}{rgb}{0,0,0} 
\colorlet{thisTextColor}{myTextColour}
\color{thisTextColor} % Whitish


%  CHange Link Colour!!!!!!!!!!!!!!!!



\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=myTextColour,
    filecolor=magenta,      
    urlcolor=blue,
}

\urlstyle{same}


\setlength{\parindent}{0pt}
\setlength{\parskip}{0.7em}






\begin{document}
\begin{titlepage}
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{0pt}
    \vspace*{\stretch{1}}
    \begin{center}
        \vspace{-4cm}
        \huge University of Cape Town
    \end{center}
    \vspace{2.5cm}
    \begin{flushleft}
        \large \texttt{EEE4022S - Final Year Project}\\[8pt]
    \end{flushleft}

    \rule{\linewidth}{0.5pt}
    \begin{center}
    \vspace{10pt}
    \huge \textbf{Spacial and Temporal Calibration of Multi-Sensor Systems}\\[5pt]
    \rule{\linewidth}{0.5pt} \\[25pt]
    \LARGE Michael Katsoulis\\[5pt]
    \large \texttt{KTSMIC005} \\[1cm]
    24 June 2020\\ %                                Date
    % !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!Check Date!!!!!!!!!!!!!!!!!!!!!!!!!!!
    \rule{5cm}{0.5pt}\\[-5pt]
    \rule{2.7cm}{0.5pt}
    \end{center}
    \vspace*{\stretch{1}}
    \Large{ \textbf{Plagerism Declaration}}

    \hrulefill
    \normalsize
    \begin{enumerate}
        \item I  know that  plagiarism is wrong. Plagiarism  is  to use  another's  work  and  pretend that  it is one's own.
        \item I  have  used  the IEEE convention  for  citation  and  referencing.  Each  contribution  to,  and quotation  in,  this final  year  project  report from  the  work(s)  of  other  people,  has  been attributed and has been cited and referenced.
        \item This project report is my own work.
        \item I have not allowed, and will not allow, anyone to copy my work with the intention of passing it off as their own work or part thereof.
    \end{enumerate}
    \begin{flushright}
        Michael Katsoulis\\
        22 June 2020
    \end{flushright}
    \hrulefill
\end{titlepage}
% ---------------------------------------------------------------------------
% check the date

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents
\pagebreak


\section{Introduction}

Why we want to calibrate a system
In the modern world, the need for autonomous vehicles is growing daily. They would improve the quality of human life, provide advances in science and open new opportunities. One of the problems that is being faced at the moment is that vehicles are of different shapes and sizes, this leads to the sensors on each vehicle being in different locations. 

The goal of this project is to investigate the current methods of determining the spacial as well as temporal offsets between sensors on a vehicle automatically. This would allow a decrease in calibration time, ease of manufacture as well as allow vehicles to continue to operate in the case of an unforeseen incident moving a sensor. 
This would allow for cheaper and more robust vehicles.


Same algorithm on multiple models of vehicle. 

Drones which can reconfigure in flight or continue if damaged.

Configurable vehicles which adapt to their modification.


\subsection{Research goal}


% hello world \autocite[1]{fu_lidar-camera_2020}
% \autocite[3]{nagy_--fly_2020}


\subsection{Literature Review}
\input{LiteratureReview.tex}

\bibliography{EEE4022S.bib}
\bibliographystyle{abbrv}

% \printbibliography
\end{document}